---
title: "Data @ Nite 2"
author: "Chris Hua"
date: "11/16/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
```

## Instructions

At our company, it's important to know when something is going wrong or our key business metrics are moving outside of our expectations. To this end, we set up alerts that are triggered when a metric moves outside of our expectations. These alerts allow us to be proactive in fixing problems rather than waiting for catastrophes.

The product team has asked you to follow the number of bookings per day in two key markets and alert them when the daily fluctuation is too high. For this alert, they’ve asked you to create a 30day rolling average and alert them when the daily value is above or below two standard deviations of the rolling mean.

We have provided a dataset in csv format for you to test out your alert. When you apply this alert over the past year for these two markets, how many alerts would have been triggered by this rule for each market?

## Data

```{r}
bookings <- read.csv("challenge_data.csv")
str(bookings)
bookings$ds <- as.Date(bookings$ds) 
str(bookings)
```

```{r}

```

## Visualize!

```{r}
library(dplyr)
install.packages('dplyr')

city_1 <- filter(bookings, city == "City_1")
city_2 <- filter(bookings, city == "City_2")

plot(city_2$bookings)
```

```{r}
install.packages('ggplot2')
bookings %>%
    ggplot(aes(x = ds, y = bookings)) + geom_point() + 
    facet_wrap(~ city)
```


## Outliers

```{r}
bookings %>% head
```


```{r}
install.packages('zoo')
library(zoo)
zoo::rollapply(city_1$bookings, FUN = mean, 30) %>% plot
```


```{r}
##########
#' Applies a function to subsets of a given dataset.
#' Note: sets values without sufficient data to NA.
#' Using 'step' is particularly useful for leave-one-out analysis.
#' 
#' @export
#' @name slide_apply
#' @author \href{https://github.com/stillmatic}{Chris Hua}
#' @title Use apply over a sliding window of data
#' @param data Array of data to apply the function over.
#' @param window Numeric. Number of data points in each window.
#' @param step Numeric. Number of indices to step through data by.
#' @param fun Function to apply over each window.
#' @return Array of the results from the function.
#' @examples 
#' toy <- runif(150, min=0, max=20)
#' slide_apply(toy, 30, 1, sd) # calculates 30 day moving standard deviation
slide_apply <- function (data, window, step = 1, fun, ...) 
{
    fun <- match.fun(fun)
    total <- length(data)
    window <- abs(window)
    spots <- seq(from = 1, to = (total - window + 1), by = abs(step))
    result <- rep(NA, length(spots))
    for (i in 1:length(spots)) {
        result[window + i - 1] <- fun(data[spots[i]:(spots[i] + 
            window - 1)], ...)
    }
    return(result)
}

city_1$avg <- slide_apply(city_1$bookings, 30, 1, mean, na.rm= T)
city_2$avg <- slide_apply(city_2$bookings, 30, 1, mean)

city_1$std <- slide_apply(city_1$bookings, 30, 1, sd)
city_2$std <- slide_apply(city_2$bookings, 30, 1, sd)

ggplot(data = city_1, aes(x = ds, y = bookings)) +
    geom_errorbar(aes(ymin=avg-2*std, ymax=avg+2*std), colour = "#dfc27d", width=0.05) +
	geom_point()
```

## Discuss
